##Models for Predicting Personal Exercise Manners##

<br>

####Summary####

In this report, we trained several models with the data from accelerometers on the belt, forearm, arm and dumbell, and the models are used to predict personal exercise manners.

<br>

####Data processing####

Loading data and packages, removing unused variables from the data set.

```{r, cache=TRUE}
library(caret)
data <- read.csv("pml-training.csv", na.strings=c("", "NA"), header = TRUE)
testcase <- read.csv("pml-testing.csv", header = TRUE)
data <- data[, c(8:11, 37:49, 60:68,84:86,102,113:124,140, 151:160)]
```

Cross validation and spliting data into training and testing set.

```{r, cache=TRUE}
set.seed(123)
inTrain <- createDataPartition(y=data$classe, p=0.75, list=FALSE)
training <- data[inTrain,]
testing <- data[-inTrain,]
```

<br>

####Model Building####

Here, we select the following models to apply to the training data set: boosting, linear discriminant analysis and random forest.

```{r, cache=TRUE}
require(gbm)
Fitbt <- "Fitbt.Rds"
if (file.exists(Fitbt)) {
        Fitbt <- readRDS(Fitbt)
} else {
    Fitbt <- train(classe ~., method="gbm", data=training, verbose=FALSE)
}
```

```{r, cache=TRUE}
require(MASS)
Fitlda <- "Fitlda.Rds"
if (file.exists(Fitlda)) {
        Fitlda <- readRDS(Fitlda)
} else {
    Fitlda <- train(classe ~., data=training, method="lda")
}
```

For random forest, the whole dataset takes too much memory, so here we took a subset of the training data to train the model

```{r, cache=TRUE, results='hide'}
set.seed(123)
ss <- sample(1:dim(training)[1], size = 3000, replace =FALSE)
subtrain <- training[ss,]
require(randomForest)
Fitrfsm <- "Fitrfsmall.Rds"
if (file.exists(Fitrfsm)) {
        Fitrfsm <- readRDS(Fitrfsm)
} else {
    Fitrfsm <- train(classe ~., method="rf", data=subtrain, prox=TRUE)
}

```

<br>

####Predicting####

Then we apply the models on the testing set to estimate the out of sample error.

```{r, cache=TRUE}
predbt <- predict(Fitbt, newdata=testing)
predlda <- predict(Fitlda, newdata=testing)
predrf <- predict(Fitrfsm, newdata=testing)
acc <- c(sum(predbt==testing$classe), sum(predlda==testing$classe), sum(predrf==testing$classe))/dim(testing)[1]
names(acc) <- c("boosting", "linear discriminant analysis", "random forest")
acc
```

Since the boosting model had the highest accuracy, ie, lowest error of 0.03, we apply it on the 20 test cases.

```{r, cache=TRUE}
X <- predict(Fitbt, newdata=testcase)
```

